---
title: "Assignment 4: Study design"
author: "Sivert Helland Veseth"
format: 
  html:
    number-sections: true
    toc: true
    code-fold: true
execute: 
  warning: false
editor: visual
editor_options: 
  chunk_output_type: console
bibliography: resources/referanser.bib
csl: resources/apa.csl
---

## Studier

1.  [Muscle Adaptations to Plyometric vs. Resistance Training in Untrained Young Men](https://journals.lww.com/nsca-jscr/fulltext/2008/11000/muscle_adaptations_to_plyometric_vs__resistance.12.aspx)

2.  [Effects of Plyometric and Resistance Training on Muscle Strength, Explosiveness, and Neuromuscular Function in Young Adolescent Soccer Players](https://journals.lww.com/nsca-jscr/fulltext/2018/11000/effects_of_plyometric_and_resistance_training_on.6.aspx)

3.  [A Comparison of the Effects of Short-Term Plyometric and Resistance Training on Lower-Body Muscular Performance](https://journals.lww.com/nsca-jscr/fulltext/2018/10000/a_comparison_of_the_effects_of_short_term.7.aspx)

4.  [Effects of Plyometric Training on Sonographic Characteristics of Quadriceps Muscle and Patellar Tendon, Quadriceps Strength, and Jump Height in Adolescent Female Volleyball Players](https://web-p-ebscohost-com.ezproxy.inn.no/ehost/pdfviewer/pdfviewer?vid=0&sid=6c4219d2-a393-4b87-8f3d-fe60b9c549a8%40redis)

5.  [Evaluation of Plyometric Exercise Training, Weight Training, and Their Combination on Vertical Jumping Performance and Leg Strength](https://journals.lww.com/nsca-jscr/abstract/2000/11000/evaluation_of_plyometric_exercise_training,_weight.16.aspx)

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
